--
title: "Asthma and redlining data"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(janitor)
library(readxl)
library(lubridate)
library(DT)
library(sf)
```

## Import asthma data and format headers 

```{r import}
headers <- c(
  "zipcode_or_region",
  "2016-Jan-Apr",
  "2016-May-Aug",
  "2016-Sep-Dec",
  "2017-Jan-Apr",
  "2017-May-Aug",
  "2017-Sep-Dec",
  "2018-Jan-Apr",
  "2018-May-Aug",
  "2018-Sep-Dec",
  "2019-Jan-Apr",
  "2019-May-Aug",
  "2019-Sep-Dec"
)

asthma_oak <- read_excel(
  "data/asthma_final1.xlsx", 
  sheet = " ED & PD summary new", 
  skip = 4,
  col_names = headers)
asthma_oak
```

## Create new variable for just asthma_oak zip codes
### Filter out the Alameda County and OEP aggregate values 

```{r}
asthma_oak_zip <- asthma_oak %>% 
  filter(zipcode_or_region != "Alameda County") %>% 
  filter (zipcode_or_region != "Oakland & Emeryville & Piedmont")
```

## Import geoJSON file of zip code boundaries
### Assign a new variable from the geoJSON data

```{r}
geo_zipcode <- st_read(
  "data/Zip_Code_Boundaries.json"
)
geo_zipcode
```

## Filter out the Mills College zip code from geo_zipcode dataframe

```{r}
geo_zipcode_rm_mills <- geo_zipcode %>% 
  filter(ZIP_CODE != "94605") %>% 
  filter(ZIP_CODE != "94613")
```

## Join zip codes to make one 

```{r}
geo_zipcode_join_zips <- geo_zipcode %>% 
  filter(ZIP_CODE == "94605" | ZIP_CODE == "94613")
```

## Full join of zip codes 

```{r}
join_wo_mills <- asthma_oak_zip %>% 
  inner_join(
    geo_zipcode_rm_mills, by = c(
      "zipcode_or_region" = "ZIP_CODE"
    )
  )
```

## Filter out asthma_oak_zip dataframe to just Mills zipcodes
```{r}
asthma_oak_zip_just_mills <- asthma_oak_zip %>% 
 filter(zipcode_or_region == "94605 & 94613")
```

## Create the shape that unites 94605 and 94613 zip codes together
## Stick that shape back 

```{r}
mills_geometry <- st_sfc(st_union(geo_zipcode_join_zips))
```

## Join the asthma_oak_zip data that includes just Mills zip codes with the shape that unites 94605 and 94613 geometries together 
```{r}
join_w_mills <- merge(asthma_oak_zip_just_mills, mills_geometry)
join_w_mills
```

## Create final dataset by binding Mills and non-Mills together and explaining to R that the geometry column means creating a shape 
```{r}
asthma_oak_geo <- st_as_sf(bind_rows(join_wo_mills, join_w_mills),
                           crs = 4326)
asthma_oak_geo
```

## Import geoJSON file of redline data
### Assign a new variable from the geoJSON redline data

```{r}
geo_redline <- read_sf(
  "data/redline/CAOakland1937.geojson"
)
geo_redline
```

# Analysis
## Is there a way to join geo_zipcode and geo_redline data and then plot?
### Which redlined neighborhoods appear in which zip codes? Are the areas with the highest amount of asthma cases in formerly redlined neighborhoods? 

## Does the geometry column value of geo_redline intersect with asthma_oak_geo, if so, smush them together
```{r}
geo_redline_zip <- st_join(geo_redline, asthma_oak_geo, join = st_intersects)
geo_redline_zip
```

## Look at C and D areas to see trends in redlining 
```{r}
cols <- c("zipcode_or_region", "holc_grade")
geo_redline_zip %>%
  group_by(across(all_of(cols))) %>% 
  summarize(total_grade = n()) %>%
  arrange(zipcode_or_region, desc(total_grade)) %>% 
  filter(zipcode_or_region == "94621")
```

