---
title: "Pollution data"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(janitor)
library(readxl)
library(lubridate)
library(DT)
library(sf)
```

```{r}
headers <- c(

  "2016-Jan-Apr",
  "2016-May-Aug",
  "2016-Sep-Dec",
  "2017-Jan-Apr",
  "2017-May-Aug",
  "2017-Sep-Dec",
  "2018-Jan-Apr",
  "2018-May-Aug",
  "2018-Sep-Dec"
)
```

# Define AQI groups by air quality 

```{r}
AQI_names <- c("Good", "Moderate", "Unhealthy for Sensitive Groups", "Unhealthy", "Very Unhealthy")
```

# OZONE DATA
## Ozone 2016 Data 
```{r}
# Define site IDs: oakland, oakland west, laney
site_ids <- c("060010009", "060010011", "060010012")
oak_oz_16 <- read_csv(
  "data/ozone_2016.csv"
  )%>% 

# Filter by site ID   
filter(`Site ID` %in% site_ids) %>% 

# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 

# create a year column
  mutate(year = format(Date, "%Y")
         ) %>% 
  
## filtering by date 01/01/16 - 04/30/16
  
  mutate(Date_Grp = case_when(
   Date >= "2016-01-01" & Date <= "2016-04-30" ~ "Jan-Apr",
   Date >= "2016-05-01" & Date <= "2016-08-31" ~ "May-Aug",
   Date >= "2016-09-01" & Date <= "2016-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 
  
## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_oz_16
```
# Add a pivot table for ozone 2016 data
```{r}
oak_oz_16 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# Ozone 2017 data
## Filter by site 
```{r}
## Define site IDs: oakland, oakland west, laney
site_ids <- c("060010009", "060010011", "060010012")
oak_oz_17 <- read_csv(
  "data/ozone_2017.csv"
  ) %>% 

## Filter by site ID   
  filter(`Site ID` %in% site_ids) %>% 

## Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 

## create a year column
  mutate(year = format(Date, "%Y")
         ) %>% 
    
## filtering by date 01/01/17 - 04/30/17
  
  mutate(Date_Grp = case_when(
   Date >= "2017-01-01" & Date <= "2017-04-30" ~ "Jan-Apr",
   Date >= "2017-05-01" & Date <= "2017-08-31" ~ "May-Aug",
   Date >= "2017-09-01" & Date <= "2017-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )  
oak_oz_17
```
## Create a pivot table
```{r}
oak_oz_17 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# Ozone 2018 Data
## Filter by site 
```{r}
## Define SiteIDs: oakland, oakland west, laney
site_ids <- c("060010009", "060010011", "060010012")
oak_oz_18 <- read_csv(
  "data/ozone_2018.csv"
  ) %>% 
  
## Create SiteID filter
filter(`Site ID` %in% site_ids) %>% 

# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 
    
# create a year column
mutate(year = format(Date, "%Y")
       ) %>% 
  
## filtering by date 01/01/18 - 04/30/18
  
  mutate(Date_Grp = case_when(
   Date >= "2018-01-01" & Date <= "2018-04-30" ~ "Jan-Apr",
   Date >= "2018-05-01" & Date <= "2018-08-31" ~ "May-Aug",
   Date >= "2018-09-01" & Date <= "2018-12-31" ~ "Sept-Dec",
   )
   ) %>%
    
## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_oz_18
```
## Create a pivot table 
```{r}
oak_oz_18 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```
# Ozone 2019 Data
## Filter by site 
```{r}
# Define SiteID: oakland, oakland west, laney
site_ids <- c("060010009", "060010011", "060010012")
oak_oz_19 <- read_csv(
  "data/ozone_2019.csv"
  )%>% 
  
# Filter by siteID 
  filter(`Site ID` %in% site_ids) %>% 

# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 

# create a year column
  mutate(year = format(Date, "%Y")
         ) %>% 
  
## filtering by date 01/01/19 - 04/30/19
  
  mutate(Date_Grp = case_when(
   Date >= "2019-01-01" & Date <= "2019-04-30" ~ "Jan-Apr",
   Date >= "2019-05-01" & Date <= "2019-08-31" ~ "May-Aug",
   Date >= "2019-09-01" & Date <= "2019-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_oz_19
```
## Create a pivot table
```{r}
oak_oz_19 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```
#PM DATA
##PM 2016 Data
```{r}
# Define Site IDs: oakland, oakland west, laney
site_ids <- c("060010009", "060010011", "060010012")
oak_pm_16 <- read_csv(
  "data/PM25_2016.csv"
  ) %>% 

## Filter by SiteID 
  
filter(`Site ID` %in% site_ids) %>% 
  
# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>%
  
# create a year column
  mutate(year = format(Date, "%Y")
         ) %>% 

## filtering by date 01/01/16 - 04/30/16
  
  mutate(Date_Grp = case_when(
   Date >= "2016-01-01" & Date <= "2016-04-30" ~ "Jan-Apr",
   Date >= "2016-05-01" & Date <= "2016-08-31" ~ "May-Aug",
   Date >= "2016-09-01" & Date <= "2016-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_pm_16
```
## Create a pivot table 
```{r}
oak_pm_16 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# PM2.5 2017 Data
## All the coding for PM2.5 2017 data 
```{r}
## Define site IDs: oakland, oakland west, laney
site_ids <- c("060010009", "060010011", "060010012")

## Read CSV 

oak_pm_17 <- read_csv(
  "data/PM25_2017.csv"
  ) %>% 

## Filter by SiteID
  filter(`Site ID` %in% site_ids) %>% 
  
# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>%
  
# create a year column
  mutate(year = format(Date, "%Y")) %>% 

## filtering by date 01/01/17 - 04/30/17
  
  mutate(Date_Grp = case_when(
   Date >= "2017-01-01" & Date <= "2017-04-30" ~ "Jan-Apr",
   Date >= "2017-05-01" & Date <= "2017-08-31" ~ "May-Aug",
   Date >= "2017-09-01" & Date <= "2017-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 
  
## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_pm_17
```
## Create a pivot table based on PM 2017 data
```{r}
oak_pm_17 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# PM2.5 2018
## All the programming for PM2.5 2018
```{r}
# Define site IDs for oakland, oakland west, laney
site_ids <- c("060010009", "060010011", "060010012")
oak_pm_18 <- read_csv(
  "data/PM25_2018.csv"
  ) %>% 
  
## Filter by SiteID
filter(`Site ID` %in% site_ids) %>% 

# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>%
  
# create a year column
  mutate(year = format(Date, "%Y")) %>% 
  
## filtering by date 01/01/18 - 04/30/18
  
  mutate(Date_Grp = case_when(
   Date >= "2018-01-01" & Date <= "2018-04-30" ~ "Jan-Apr",
   Date >= "2018-05-01" & Date <= "2018-08-31" ~ "May-Aug",
   Date >= "2018-09-01" & Date <= "2018-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )

oak_pm_18
```

## Create a pivot table based on PM 2018 data
```{r}
oak_pm_18 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# PM2.5 2019 Data
## All the programming in one for PM 2019 
```{r}
# Define site IDs: oakland, oakland west, laney

site_ids <- c("060010009", "060010011", "060010012")
oak_pm_19 <- read_csv(
  "data/PM25_2019.csv"
  ) %>% 

# Filter by site ID   
  filter(`Site ID` %in% site_ids) %>% 
  
# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 

# create a year column
  mutate(year = format(Date, "%Y")) %>% 

## filtering by date 01/01/19 - 04/30/19
  
  mutate(Date_Grp = case_when(
   Date >= "2019-01-01" & Date <= "2019-04-30" ~ "Jan-Apr",
   Date >= "2019-05-01" & Date <= "2019-08-31" ~ "May-Aug",
   Date >= "2019-09-01" & Date <= "2019-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_pm_19
```

## Create a pivot table 
```{r}
oak_pm_19 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# NO2 2016 Data
## All the programming in one for NO2 2016
```{r}
# Define site IDs: oakland, oakland west, laney

site_ids <- c("060010009", "060010011", "060010012")
oak_no_16 <- read_csv(
  "data/NO2_2016.csv"
  ) %>% 

# Filter by site ID   
  filter(`Site ID` %in% site_ids) %>% 
  
# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 

# create a year column
  mutate(year = format(Date, "%Y")) %>% 

## filtering by date 01/01/19 - 04/30/19
  
  mutate(Date_Grp = case_when(
   Date >= "2016-01-01" & Date <= "2016-04-30" ~ "Jan-Apr",
   Date >= "2016-05-01" & Date <= "2016-08-31" ~ "May-Aug",
   Date >= "2016-09-01" & Date <= "2016-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_no_16
```

## Create a pivot table 
```{r}
oak_no_16 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# NO2 2017 Data
## All the programming in one for NO2 2017
```{r}
# Define site IDs: oakland, oakland west, laney

site_ids <- c("060010009", "060010011", "060010012")
oak_no_17 <- read_csv(
  "data/NO2_2017.csv"
  ) %>% 

# Filter by site ID   
  filter(`Site ID` %in% site_ids) %>% 
  
# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 

# create a year column
  mutate(year = format(Date, "%Y")) %>% 

## filtering by date 01/01/19 - 04/30/19
  
  mutate(Date_Grp = case_when(
   Date >= "2017-01-01" & Date <= "2017-04-30" ~ "Jan-Apr",
   Date >= "2017-05-01" & Date <= "2017-08-31" ~ "May-Aug",
   Date >= "2017-09-01" & Date <= "2017-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_no_17
```
## Create a pivot table 
```{r}
oak_no_17 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# NO2 2018
## All the programming in one for NO2 2018
```{r}
# Define site IDs: oakland, oakland west, laney

site_ids <- c("060010009", "060010011", "060010012")
oak_no_18 <- read_csv(
  "data/NO2_2018.csv"
  ) %>% 

# Filter by site ID   
  filter(`Site ID` %in% site_ids) %>% 
  
# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 

# create a year column
  mutate(year = format(Date, "%Y")) %>% 

## filtering by date 01/01/19 - 04/30/19
  
  mutate(Date_Grp = case_when(
   Date >= "2018-01-01" & Date <= "2018-04-30" ~ "Jan-Apr",
   Date >= "2018-05-01" & Date <= "2018-08-31" ~ "May-Aug",
   Date >= "2018-09-01" & Date <= "2018-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_no_18
```
## Create a pivot table 
```{r}
oak_no_18 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# NO2 2018 data
## All the programming in one for NO2 2018
```{r}
# Define site IDs: oakland, oakland west, laney

site_ids <- c("060010009", "060010011", "060010012")
oak_no_19 <- read_csv(
  "data/NO2_2019.csv"
  ) %>% 

# Filter by site ID   
  filter(`Site ID` %in% site_ids) %>% 
  
# Converting date from string (random characters) to a real date object
  mutate(Date = 
    mdy(Date)
    ) %>% 

# create a year column
  mutate(year = format(Date, "%Y")) %>% 

## filtering by date 01/01/19 - 04/30/19
  
  mutate(Date_Grp = case_when(
   Date >= "2019-01-01" & Date <= "2019-04-30" ~ "Jan-Apr",
   Date >= "2019-05-01" & Date <= "2019-08-31" ~ "May-Aug",
   Date >= "2019-09-01" & Date <= "2019-12-31" ~ "Sept-Dec",
   )) %>%

## Assign AQI value based on EPA standards 

  mutate(AQI_Grp = case_when(
    DAILY_AQI_VALUE <= 50 ~ "Good",
    DAILY_AQI_VALUE >= 51 &  DAILY_AQI_VALUE <= 100 ~ "Moderate",
    DAILY_AQI_VALUE >= 101 & DAILY_AQI_VALUE <= 150 ~ "Unhealthy for Sensitive Groups",
    DAILY_AQI_VALUE >= 151 & DAILY_AQI_VALUE <= 200 ~ "Unhealthy",
    DAILY_AQI_VALUE >= 201 ~ "Very Unhealthy"
  )) %>% 

## Grouping by year, date, and AQI group and counting number of days by AQI group  
  group_by(
  `Site ID`, `Site Name`, `year`, `Date_Grp`, `AQI_Grp`  
  ) %>% 
  summarise(
  "Total" = n()
  )
oak_no_19
```

## Create a pivot table 
```{r}
oak_no_19 %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
```

# Merge all the years of the NO2 dataframes

```{r}
all_no <- bind_rows(oak_no_16, oak_no_17, oak_no_18, oak_no_19) %>% 
  mutate(pollutant = "no"
  ) %>%
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
all_no
```

# Merge all the years of the pm dataframes 
```{r}
all_pm <- bind_rows(oak_pm_16, oak_pm_17, oak_pm_18, oak_pm_19) %>% 
  mutate(pollutant = "pm"
  ) %>%
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
all_pm
```

# Merge all the years of the ozone dataframes 

```{r}
all_oz <- bind_rows(oak_oz_16, oak_oz_17, oak_oz_18, oak_oz_19) %>% 
  mutate(pollutant = "ozone"
  ) %>% 
  pivot_wider(
    names_from = AQI_Grp,
    values_from = Total
  )
all_oz
```

# Smush the dataframes today 

```{r}
all_pollutants <- bind_rows (all_pm, all_oz, all_no) 
all_pollutants
```

## Totals for the dataframes 

```{r}
sum(all_pollutants$Good)
```

# Stats for story

```{r}
colSums(Filter(is.numeric, all_pollutants), na.rm = TRUE)
```

# Can edit the group_by statement to see different cuts of the data, summed up

```{r}
all_pollutants %>%
  group_by(
    `Site Name`, `pollutant` 
  ) %>% 
  summarise_at(
    AQI_names, sum, na.rm = TRUE
  ) %>% 
  
## Sum all the rows that are numeric 
  mutate(total = rowSums(across(where(is.numeric))))
```

# Group by year 
```{r}
all_pollutants %>%
  group_by(
    `year`
  ) %>% 
  summarise_at(
    AQI_names, sum, na.rm = TRUE
  ) %>% 
  
## Sum all the rows that are numeric 
  mutate(total = rowSums(across(where(is.numeric))))
```

